### 2021-06-10 memo.tex
corrected wrong AHSS

\subsection{Leray-Serre SS (preparatory)}
For the fibration
\begin{equation}
	BSU(2n_f)
	\ \to\ 
	B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right)
	\ \to\ 
	BPSO(4n'_c+2)
\end{equation}
we have
\begin{equation}
	\begin{array}{ccc}
		E_2^{p,q}=H^p\big(BPSO(4n'_c+2);H^q(BSU(2n_f);\bZ)\big) && H^{p+q}(B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
		\begin{array}{c|ccccccccccccc}
			6  & \bZ &&& \ast & \ast && \ast\\
			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
			4  & \bZ & \cellcolor{lightyellow} && \ast & \ast & & \ast\\
			3  &  && \cellcolor{lightyellow} &&&\\
			2  &&  && \cellcolor{lightyellow} &&\\
			1  &  &&  && \cellcolor{lightyellow} &&\\
			0 & \bZ &  && \bZ_4 & \bZ & \cellcolor{lightyellow} & \bZ_2^{\oplus 2}\\
			\hline
			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
		\end{array}
		& \longrightarrow & 
		\begin{array}{c|c}
			6  & \bZ\oplus \bZ_2^{\oplus 2}\\
			5  & \cellcolor{lightyellow}\\
			4  & \bZ^{\oplus 2}\\
			3  & \bZ_4\\
			2  & \\
			1  & \\
			0 & \bZ\\
			\hline\\
		\end{array}
	\end{array}
\end{equation}

\subsection{Atiyah-Hirzebruch SS}
Having obtained (co)homology groups,
one can fill in the $E^2$-page of the AHSS:
\begin{equation}
	\begin{array}{c}
		E^2_{p,q}=H_p\big(B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right);\Omega_q^{\text{spin}}\big)\vspace{2mm}\\
		\begin{array}{c|c:cccccccccccc}
			6  &&&&&& \\
			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
			4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
			3  &  && \cellcolor{lightyellow} &&&\\
			2  & \bZ_2 &  & \red{\dbox{\black{$\bZ_2$}}} & \Blue{\dbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \ast & \ast & \ast\\
			1  & \bZ_2 && \red{\fbox{\black{$\bZ_2$}}} & \Blue{\fbox{\black{$\bZ_2$}}} & \green{\fbox{\black{\red{\dbox{\black{$\bZ_2^{\oplus 2}$}}}}}}\cellcolor{lightyellow} & \Blue{\dbox{\black{$\ast$}}} & \ast\\
			0 & \bZ &  & \bZ_4 &  & \red{\fbox{\black{$\bZ^{\oplus 2}$}}} & \Blue{\fbox{\black{$\bZ_2^{\oplus 2}$}}}\cellcolor{lightyellow} & \green{\fbox{\black{$\ast$}}}\\
			\hline
			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
		\end{array}
	\end{array}
\end{equation}
Based on our belief, 
\red{\fbox{\black{$d^2 : E^2_{4,0} \to E^2_{2,1}$}}} and
\red{\dbox{\black{$d^2 : E^2_{4,1} \to E^2_{2,2}$}}} should be a dual of
\begin{equation}
	\begin{array}{ccccc}
		Sq^2 a_2 & = & (a_2)^2
	\end{array}
\end{equation}
and also
\Blue{\fbox{\black{$d^2 : E^2_{5,0} \to E^2_{3,1}$}}} and
\Blue{\dbox{\black{$d^2 : E^2_{5,1} \to E^2_{3,2}$}}} should be a dual of
\begin{equation}
	\begin{array}{ccccc}
		Sq^2 y'(1) & = & y'(2)\\
	\end{array}
\end{equation}
and finally
\green{\fbox{\black{$d^2 : E^2_{6,0} \to E^2_{4,1}$}}} should be a dual of
\begin{equation}
	\begin{array}{ccccc}
		Sq^2 c_2 & = & c_3
	\end{array}
\end{equation}
then %one can proceed, and 
the would-be-$E_3$-page is given by
\begin{equation}
	\begin{array}{c|c:cccccccccccc}
		6  &&&&&& \\
		5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
		4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
		3  &  && \cellcolor{lightyellow} &&&& \hphantom{\bZ_2}\\
		2  & \bZ_2 &&& \cellcolor{lightyellow} & \ast & \ast & \ast\\
		1  & \bZ_2 &&&& \cellcolor{lightyellow} & \ast & \ast\\
		0 & \bZ &  & \bZ_4 &  & \bZ^{\oplus 2} & \bZ_2\cellcolor{lightyellow} & \ast\\
		\hline
		& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
	\end{array}
\end{equation}

>>>>

\subsection{Leray-Serre SS (preparatory)}
For the fibration
\begin{equation}
	BSU(2n_f)
	\ \to\ 
	B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right)
	\ \to\ 
	BPSO(4n'_c+2)
\end{equation}
we have
\begin{equation}
	\begin{array}{ccc}
		E_2^{p,q}=H^p\big(BPSO(4n'_c+2);H^q(BSU(2n_f);\bZ)\big) && H^{p+q}(B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right);\bZ)\vspace{4mm}\\
		\begin{array}{c|ccccccccccccc}
			6  & \bZ &&& \ast & \ast && \ast\\
			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
			4  & \bZ & \cellcolor{lightyellow} && \ast & \ast & & \ast\\
			3  &  && \cellcolor{lightyellow} &&&\\
			2  &&  && \cellcolor{lightyellow} &&\\
			1  &  &&  && \cellcolor{lightyellow} &&\\
			0 & \bZ &  && \bZ_4 & \bZ & \cellcolor{lightyellow} & \bZ_2\\
			\hline
			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
		\end{array}
		& \longrightarrow & 
		\begin{array}{c|c}
			6  & \bZ\oplus \bZ_2\\
			5  & \cellcolor{lightyellow}\\
			4  & \bZ^{\oplus 2}\\
			3  & \bZ_4\\
			2  & \\
			1  & \\
			0 & \bZ\\
			\hline\\
		\end{array}
	\end{array}
\end{equation}

\subsection{Atiyah-Hirzebruch SS}
Having obtained (co)homology groups,
one can fill in the $E^2$-page of the AHSS:
\begin{equation}
	\begin{array}{c}
		E^2_{p,q}=H_p\big(B\left(\tfrac{SO(4n'_c+2)\times SU(2n_f)}{\bZ_2}\right);\Omega_q^{\text{spin}}\big)\vspace{2mm}\\
		\begin{array}{c|c:cccccccccccc}
			6  &&&&&& \\
			5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
			4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
			3  &  && \cellcolor{lightyellow} &&&\\
			2  & \bZ_2 &  & \red{\dbox{\black{$\bZ_2$}}} & \Blue{\dbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \ast & \ast & \ast\\
			1  & \bZ_2 && \red{\fbox{\black{$\bZ_2$}}} & \Blue{\fbox{\black{$\bZ_2$}}} & \green{\fbox{\black{\red{\dbox{\black{$\bZ_2^{\oplus 2}$}}}}}}\cellcolor{lightyellow} & \Blue{\dbox{\black{$\ast$}}} & \ast\\
			0 & \bZ &  & \bZ_4 &  & \red{\fbox{\black{$\bZ^{\oplus 2}$}}} & \Blue{\fbox{\black{$\bZ_2$}}}\cellcolor{lightyellow} & \green{\fbox{\black{$\ast$}}}\\
			\hline
			& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
		\end{array}
	\end{array}
\end{equation}
Based on our belief, 
\red{\fbox{\black{$d^2 : E^2_{4,0} \to E^2_{2,1}$}}} and
\red{\dbox{\black{$d^2 : E^2_{4,1} \to E^2_{2,2}$}}} should be a dual of
\begin{equation}
	\begin{array}{ccccc}
		Sq^2 a_2 & = & (a_2)^2
	\end{array}
\end{equation}
and also
\Blue{\fbox{\black{$d^2 : E^2_{5,0} \to E^2_{3,1}$}}} and
\Blue{\dbox{\black{$d^2 : E^2_{5,1} \to E^2_{3,2}$}}} should be a dual of
\begin{equation}
	\begin{array}{ccccc}
		Sq^2 y'(1) & = & y'(2)\\
	\end{array}
\end{equation}
and finally
\green{\fbox{\black{$d^2 : E^2_{6,0} \to E^2_{4,1}$}}} should be a dual of
\begin{equation}
	\begin{array}{ccccc}
		Sq^2 c_2 & = & c_3
	\end{array}
\end{equation}
then %one can proceed, and 
the would-be-$E_3$-page is given by
\begin{equation}
	\begin{array}{c|c:cccccccccccc}
		6  &&&&&& \\
		5  & \cellcolor{lightyellow} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} & \hphantom{\bZ_2} \\
		4  & \bZ & \cellcolor{lightyellow} & \ast && \ast & \ast & \ast\\
		3  &  && \cellcolor{lightyellow} &&&& \hphantom{\bZ_2}\\
		2  & \bZ_2 &&& \cellcolor{lightyellow} & \ast & \ast & \ast\\
		1  & \bZ_2 &&&& \cellcolor{lightyellow} & \ast & \ast\\
		0 & \bZ &  & \bZ_4 &  & \bZ^{\oplus 2} & \cellcolor{lightyellow} & \ast\\
		\hline
		& 0 & 1 & 2 & 3 & 4 & 5 & 6 \\
	\end{array}
\end{equation}
